---
title: "Processing_COLONY_output_juveniles"
author: "Hayley Nuetzel"
date: "2/12/2021"
output: html_document
---

```{r}
rm(list = ls())
library(tidyverse)
```


```{r}
#read in COLONY results
#Juvs 2009
juvs2009 <- read_csv("COLONY2_Results/LKG_2009Juvs_Aug2021/LKG_2009Juvs_Aug2021_BestCluster.csv")
#codes to CRITFC_ID
juvs2009_codes <- read_csv("COLONY2_Run_Files/Juvs2009/LKG_2009Juvs_IDcodes.csv")

#join to codes
juvs2009_convert <- left_join(juvs2009, juvs2009_codes, by = c("OffspringID" = "COLONY_ID")) %>%
  dplyr::select(., -OffspringID) %>%
  dplyr::rename(., OffspringID = Progeny_ID) %>%
  left_join(., juvs2009_codes, by = c("FatherID" = "COLONY_ID")) %>%
  mutate(., Parent1 = ifelse(is.na(Progeny_ID), FatherID, Progeny_ID)) %>%
  dplyr::select(., -FatherID, -Progeny_ID) %>%
  left_join(., juvs2009_codes, by = c("MotherID" = "COLONY_ID")) %>%
  mutate(., Parent2 = ifelse(is.na(Progeny_ID), MotherID, Progeny_ID)) %>%
  dplyr::select(., -MotherID, - Progeny_ID) %>%
  mutate(., OffspringSampleYear = "Juv_2009")
```


```{r}
#read in COLONY results
#Juvs 2010
juvs2010 <- read_csv("COLONY2_Results/LKG_2010Juvs_Aug2021/LKG_2010Juvs_Aug2021_BestCluster.csv")
#codes to CRITFC_ID
juvs2010_codes <- read_csv("COLONY2_Run_Files/Juvs2010/LKG_2010Juvs_IDcodes.csv")

#join to codes
juvs2010_convert <- left_join(juvs2010, juvs2010_codes, by = c("OffspringID" = "COLONY_ID")) %>%
  dplyr::select(., -OffspringID) %>%
  dplyr::rename(., OffspringID = Progeny_ID) %>%
  left_join(., juvs2010_codes, by = c("FatherID" = "COLONY_ID")) %>%
  mutate(., Parent1 = ifelse(is.na(Progeny_ID), FatherID, Progeny_ID)) %>%
  dplyr::select(., -FatherID, -Progeny_ID) %>%
  left_join(., juvs2010_codes, by = c("MotherID" = "COLONY_ID")) %>%
  mutate(., Parent2 = ifelse(is.na(Progeny_ID), MotherID, Progeny_ID)) %>%
  dplyr::select(., -MotherID, - Progeny_ID) %>%
  mutate(., OffspringSampleYear = "Juv_2010")
```


```{r}
#read in COLONY results
#Juvs 2011
juvs2011 <- read_csv("COLONY2_Results/LKG_2011Juvs_Aug2021/LKG_2011Juvs_Aug2021_BestCluster.csv")
#codes to CRITFC_ID
juvs2011_codes <- read_csv("COLONY2_Run_Files/Juvs2011/LKG_2011Juvs_IDcodes.csv")

#join to codes
juvs2011_convert <- left_join(juvs2011, juvs2011_codes, by = c("OffspringID" = "COLONY_ID")) %>%
  dplyr::select(., -OffspringID) %>%
  dplyr::rename(., OffspringID = Progeny_ID) %>%
  left_join(., juvs2011_codes, by = c("FatherID" = "COLONY_ID")) %>%
  mutate(., Parent1 = ifelse(is.na(Progeny_ID), FatherID, Progeny_ID)) %>%
  dplyr::select(., -FatherID, -Progeny_ID) %>%
  left_join(., juvs2011_codes, by = c("MotherID" = "COLONY_ID")) %>%
  mutate(., Parent2 = ifelse(is.na(Progeny_ID), MotherID, Progeny_ID)) %>%
  dplyr::select(., -MotherID, - Progeny_ID) %>%
  mutate(., OffspringSampleYear = "Juv_2011")
```


```{r}
#read in COLONY results
#Juvs 2012
juvs2012 <- read_csv("COLONY2_Results/LKG_2012Juvs_Aug2021/LKG_2012Juvs_Aug2021_BestCluster.csv")
#codes to CRITFC_ID
juvs2012_codes <- read_csv("COLONY2_Run_Files/Juvs2012/LKG_2012Juvs_IDcodes.csv")

#join to codes
juvs2012_convert <- left_join(juvs2012, juvs2012_codes, by = c("OffspringID" = "COLONY_ID")) %>%
  dplyr::select(., -OffspringID) %>%
  dplyr::rename(., OffspringID = Progeny_ID) %>%
  left_join(., juvs2012_codes, by = c("FatherID" = "COLONY_ID")) %>%
  mutate(., Parent1 = ifelse(is.na(Progeny_ID), FatherID, Progeny_ID)) %>%
  dplyr::select(., -FatherID, -Progeny_ID) %>%
  left_join(., juvs2012_codes, by = c("MotherID" = "COLONY_ID")) %>%
  mutate(., Parent2 = ifelse(is.na(Progeny_ID), MotherID, Progeny_ID)) %>%
  dplyr::select(., -MotherID, - Progeny_ID) %>%
  mutate(., OffspringSampleYear = "Juv_2012")
```


```{r}
#read in COLONY results
#Juvs 2013
juvs2013 <- read_csv("COLONY2_Results/LKG_2013Juvs_Aug2021/LKG_2013Juvs_Aug2021_BestCluster.csv")
#codes to CRITFC_ID
juvs2013_codes <- read_csv("COLONY2_Run_Files/Juvs2013/LKG_2013Juvs_IDcodes.csv")

#join to codes
juvs2013_convert <- left_join(juvs2013, juvs2013_codes, by = c("OffspringID" = "COLONY_ID")) %>%
  dplyr::select(., -OffspringID) %>%
  dplyr::rename(., OffspringID = Progeny_ID) %>%
  left_join(., juvs2013_codes, by = c("FatherID" = "COLONY_ID")) %>%
  mutate(., Parent1 = ifelse(is.na(Progeny_ID), FatherID, Progeny_ID)) %>%
  dplyr::select(., -FatherID, -Progeny_ID) %>%
  left_join(., juvs2013_codes, by = c("MotherID" = "COLONY_ID")) %>%
  mutate(., Parent2 = ifelse(is.na(Progeny_ID), MotherID, Progeny_ID)) %>%
  dplyr::select(., -MotherID, - Progeny_ID) %>%
  mutate(., OffspringSampleYear = "Juv_2013")
```


```{r}
#read in COLONY results
#Juvs 2014
juvs2014 <- read_csv("COLONY2_Results/LKG_2014Juvs_Aug2021/LKG_2014Juvs_Aug2021_BestCluster.csv")
#codes to CRITFC_ID
juvs2014_codes <- read_csv("COLONY2_Run_Files/Juvs2014/LKG_2014Juvs_IDcodes.csv")

#join to codes
juvs2014_convert <- left_join(juvs2014, juvs2014_codes, by = c("OffspringID" = "COLONY_ID")) %>%
  dplyr::select(., -OffspringID) %>%
  dplyr::rename(., OffspringID = Progeny_ID) %>%
  left_join(., juvs2014_codes, by = c("FatherID" = "COLONY_ID")) %>%
  mutate(., Parent1 = ifelse(is.na(Progeny_ID), FatherID, Progeny_ID)) %>%
  dplyr::select(., -FatherID, -Progeny_ID) %>%
  left_join(., juvs2014_codes, by = c("MotherID" = "COLONY_ID")) %>%
  mutate(., Parent2 = ifelse(is.na(Progeny_ID), MotherID, Progeny_ID)) %>%
  dplyr::select(., -MotherID, - Progeny_ID) %>%
  mutate(., OffspringSampleYear = "Juv_2014")
```


```{r}
#read in COLONY results
#Juvs 2015
juvs2015 <- read_csv("COLONY2_Results/LKG_2015Juvs_Aug2021/LKG_2015Juvs_Aug2021_BestCluster.csv")
#codes to CRITFC_ID
juvs2015_codes <- read_csv("COLONY2_Run_Files/Juvs2015/LKG_2015Juvs_IDcodes.csv")

#join to codes
juvs2015_convert <- left_join(juvs2015, juvs2015_codes, by = c("OffspringID" = "COLONY_ID")) %>%
  dplyr::select(., -OffspringID) %>%
  dplyr::rename(., OffspringID = Progeny_ID) %>%
  left_join(., juvs2015_codes, by = c("FatherID" = "COLONY_ID")) %>%
  mutate(., Parent1 = ifelse(is.na(Progeny_ID), FatherID, Progeny_ID)) %>%
  dplyr::select(., -FatherID, -Progeny_ID) %>%
  left_join(., juvs2015_codes, by = c("MotherID" = "COLONY_ID")) %>%
  mutate(., Parent2 = ifelse(is.na(Progeny_ID), MotherID, Progeny_ID)) %>%
  dplyr::select(., -MotherID, - Progeny_ID) %>%
  mutate(., OffspringSampleYear = "Juv_2015")
```


```{r}
#read in COLONY results
#Juvs 2016
juvs2016 <- read_csv("COLONY2_Results/LKG_2016Juvs_Aug2021/LKG_2016Juvs_Aug2021_BestCluster.csv")
#codes to CRITFC_ID
juvs2016_codes <- read_csv("COLONY2_Run_Files/Juvs2016/LKG_2016Juvs_IDcodes.csv")

#join to codes
juvs2016_convert <- left_join(juvs2016, juvs2016_codes, by = c("OffspringID" = "COLONY_ID")) %>%
  dplyr::select(., -OffspringID) %>%
  dplyr::rename(., OffspringID = Progeny_ID) %>%
  left_join(., juvs2016_codes, by = c("FatherID" = "COLONY_ID")) %>%
  mutate(., Parent1 = ifelse(is.na(Progeny_ID), FatherID, Progeny_ID)) %>%
  dplyr::select(., -FatherID, -Progeny_ID) %>%
  left_join(., juvs2016_codes, by = c("MotherID" = "COLONY_ID")) %>%
  mutate(., Parent2 = ifelse(is.na(Progeny_ID), MotherID, Progeny_ID)) %>%
  dplyr::select(., -MotherID, - Progeny_ID) %>%
  mutate(., OffspringSampleYear = "Juv_2016")
```


```{r}
#read in COLONY results
#Juvs 2017
juvs2017 <- read_csv("COLONY2_Results/LKG_2017Juvs_Aug2021/LKG_2017Juvs_Aug2021_BestCluster.csv")
#codes to CRITFC_ID
juvs2017_codes <- read_csv("COLONY2_Run_Files/Juvs2017/LKG_2017Juvs_IDcodes.csv")

#join to codes
juvs2017_convert <- left_join(juvs2017, juvs2017_codes, by = c("OffspringID" = "COLONY_ID")) %>%
  dplyr::select(., -OffspringID) %>%
  dplyr::rename(., OffspringID = Progeny_ID) %>%
  left_join(., juvs2017_codes, by = c("FatherID" = "COLONY_ID")) %>%
  mutate(., Parent1 = ifelse(is.na(Progeny_ID), FatherID, Progeny_ID)) %>%
  dplyr::select(., -FatherID, -Progeny_ID) %>%
  left_join(., juvs2017_codes, by = c("MotherID" = "COLONY_ID")) %>%
  mutate(., Parent2 = ifelse(is.na(Progeny_ID), MotherID, Progeny_ID)) %>%
  dplyr::select(., -MotherID, - Progeny_ID) %>%
  mutate(., OffspringSampleYear = "Juv_2017")
```


```{r}
#read in COLONY results
#Juvs 2018
juvs2018 <- read_csv("COLONY2_Results/LKG_2018Juvs_Aug2021/LKG_2018Juvs_Aug2021_BestCluster.csv")
#codes to CRITFC_ID
juvs2018_codes <- read_csv("COLONY2_Run_Files/Juvs2018/LKG_2018Juvs_IDcodes.csv")

#join to codes
juvs2018_convert <- left_join(juvs2018, juvs2018_codes, by = c("OffspringID" = "COLONY_ID")) %>%
  dplyr::select(., -OffspringID) %>%
  dplyr::rename(., OffspringID = Progeny_ID) %>%
  left_join(., juvs2018_codes, by = c("FatherID" = "COLONY_ID")) %>%
  mutate(., Parent1 = ifelse(is.na(Progeny_ID), FatherID, Progeny_ID)) %>%
  dplyr::select(., -FatherID, -Progeny_ID) %>%
  left_join(., juvs2018_codes, by = c("MotherID" = "COLONY_ID")) %>%
  mutate(., Parent2 = ifelse(is.na(Progeny_ID), MotherID, Progeny_ID)) %>%
  dplyr::select(., -MotherID, - Progeny_ID) %>%
  mutate(., OffspringSampleYear = "Juv_2018")
```


```{r}
#read in COLONY results
#Juvs 2019
juvs2019 <- read_csv("COLONY2_Results/LKG_2019Juvs_Aug2021/LKG_2019Juvs_Aug2021_BestCluster.csv")
#codes to CRITFC_ID
juvs2019_codes <- read_csv("COLONY2_Run_Files/Juvs2019/LKG_2019Juvs_IDcodes.csv")

#join to codes
juvs2019_convert <- left_join(juvs2019, juvs2019_codes, by = c("OffspringID" = "COLONY_ID")) %>%
  dplyr::select(., -OffspringID) %>%
  dplyr::rename(., OffspringID = Progeny_ID) %>%
  left_join(., juvs2019_codes, by = c("FatherID" = "COLONY_ID")) %>%
  mutate(., Parent1 = ifelse(is.na(Progeny_ID), FatherID, Progeny_ID)) %>%
  dplyr::select(., -FatherID, -Progeny_ID) %>%
  left_join(., juvs2019_codes, by = c("MotherID" = "COLONY_ID")) %>%
  mutate(., Parent2 = ifelse(is.na(Progeny_ID), MotherID, Progeny_ID)) %>%
  dplyr::select(., -MotherID, - Progeny_ID) %>%
  mutate(., OffspringSampleYear = "Juv_2019")
```


```{r}
#read in COLONY results
#Juvs 2020
juvs2020 <- read_csv("COLONY2_Results/LKG_2020Juvs_Aug2021/LKG_2020Juvs_Aug2021_BestCluster.csv")
#codes to CRITFC_ID
juvs2020_codes <- read_csv("COLONY2_Run_Files/Juvs2020/LKG_2020Juvs_IDcodes.csv")

#join to codes
juvs2020_convert <- left_join(juvs2020, juvs2020_codes, by = c("OffspringID" = "COLONY_ID")) %>%
  dplyr::select(., -OffspringID) %>%
  dplyr::rename(., OffspringID = Progeny_ID) %>%
  left_join(., juvs2020_codes, by = c("FatherID" = "COLONY_ID")) %>%
  mutate(., Parent1 = ifelse(is.na(Progeny_ID), FatherID, Progeny_ID)) %>%
  dplyr::select(., -FatherID, -Progeny_ID) %>%
  left_join(., juvs2020_codes, by = c("MotherID" = "COLONY_ID")) %>%
  mutate(., Parent2 = ifelse(is.na(Progeny_ID), MotherID, Progeny_ID)) %>%
  dplyr::select(., -MotherID, - Progeny_ID) %>%
  mutate(., OffspringSampleYear = "Juv_2020")
```



```{r}
#combine all together
juvs_all <- bind_rows(juvs2009_convert, juvs2010_convert, juvs2011_convert, juvs2012_convert, juvs2013_convert, juvs2014_convert, juvs2015_convert, juvs2016_convert, juvs2017_convert, juvs2018_convert, juvs2019_convert, juvs2020_convert) %>%
  arrange(., Probability)

#want to do a quick plot of probabilities to see if there are obvious breakpoints
#create probability distribution plot
p <- ggplot(juvs_all, aes(sample = Probability))
p + stat_qq() + scale_y_continuous(breaks = seq(0,1,0.10)) #copy line directly into console

#pretty precipitous decline from 1.0 down to 0.0
#majority of the assignments in the 0.90 - 1.0 window 
#want to just look at those with Prob > 0.90 
juvs_all_Prob_0.9 <- filter(juvs_all, Probability >= 0.9)
q <- ggplot(juvs_all_Prob_0.9, aes(sample = Probability))
q + stat_qq() + scale_y_continuous(breaks = seq(0.9,1,0.10)) #copy line directly into console

#unlike the adults, there is a more obvious stutter around Prob ~0.925. But since we used 0.90 for the adult assignments, will just use that here as well. 
juvs_all_COLONY_filter <- filter(juvs_all, Probability >= 0.90)

```


Like with the adult assignments, all potential parents were considered as both dams and sires (i.e., didn't assign potential parents sex) for the juveniles as offspring. So we need to combine these filtered assignments back to metadata to identify Parents as either dams or sires, and categorize accordingly. First we are going to use the sex assignments identified by going through the COLONY adult assignments (which were also built upon the SNPPIT assignments) by eye and then fill in with original metadata as needed. 


```{r}

COLONY_AdultAssign_sex_list <- read_csv("COLONY2_Results/Parent_Sex_Assign_by_COLONY_Adult_results.csv")

#now combine to the filtered COLONY juvenile assignments, Par1 first
juvs_COLONY_filter_Par1 <- left_join(juvs_all_COLONY_filter, COLONY_AdultAssign_sex_list, by = c("Parent1" = "Progeny_ID")) %>%
  rename(., Parent1_Sex = Sex)

#then for Parent2
juvs_COLONY_filter_Par2 <- left_join(juvs_COLONY_filter_Par1, COLONY_AdultAssign_sex_list, by = c("Parent2" = "Progeny_ID")) %>%
  rename(., Parent2_Sex = Sex)

#next consider the SNPPIT-derived metadata for filling in sex of parents that remanin unknown 
SNPPIT_sex_list <- read_csv("SNPPIT_run_files/Individ_SexUpdates_fromSNPPITassign.csv")

#now combine to the filtered COLONY assignments by Parent 1 first 
juvs_COLONY_filter_Par1_bySNPPIT <- left_join(juvs_COLONY_filter_Par2, SNPPIT_sex_list, by = c("Parent1" = "Progeny_ID")) %>%
  rename(., Parent1_bySNPPIT_Sex = Sex)

#then for Parent2
juvs_COLONY_filter_Par2_bySNPPIT <- left_join(adults_COLONY_filter_Par1_bySNPPIT, SNPPIT_sex_list, by = c("Parent2" = "Progeny_ID")) %>%
  rename(., Parent2_bySNPPIT_Sex = Sex)

#ok now create one sex column for parents 1 and 2 based on the info combined thus far
juvs_COLONY_filter_Parent1_sex <- juvs_COLONY_filter_Par2_bySNPPIT %>%
  mutate(., Parent1_Sex_1 = ifelse(is.na(Parent1_Sex), Parent1_bySNPPIT_Sex, Parent1_Sex)) %>% #use COLONY sex first, then snppit sex
  relocate(., Parent1_Sex_1, .after = Parent1)

juvs_COLONY_filter_Parent2_sex <- juvs_COLONY_filter_Parent1_sex %>%
  mutate(., Parent2_Sex_1 = ifelse(is.na(Parent2_Sex), Parent2_bySNPPIT_Sex, Parent2_Sex)) %>% #use COLONY sex first, then snppit sex
  relocate(., Parent2_Sex_1, .after = Parent2)

#still some sampled individuals found as parents which still have unknown sex data (i.e., not found as a parent in the Adult-to-Adult colony assingment or the SNPPIT assignments)
#so have to use the original metadata for this 
#for some reason there are some duplicate entries in this so remove duplicates with unique()
metadata <- read_csv("CleanedProgenyExport/LKG_Meta_withBroodstock_Cleaned.csv") %>%
  select(., IndividualName, Gender, GenderCorrection, GeneticSex_OtsSEXY3) %>%
  unique()

#again for parent1 first
juvs_COLONY_filter_Par1_og_meta <- left_join(juvs_COLONY_filter_Parent2_sex, metadata, by = c("Parent1" = "IndividualName")) %>%
  rename(., Gender_meta_Parent1 = Gender, GenderCorrect_meta_Parent1 = GenderCorrection, GeneticSex_OtsSEXY3_Parent1 = GeneticSex_OtsSEXY3)
                                         
#then for parent2
juvs_COLONY_filter_Par2_og_meta <- left_join(juvs_COLONY_filter_Par1_og_meta, metadata, by = c("Parent2" = "IndividualName")) %>%
  rename(., Gender_meta_Parent2 = Gender, GenderCorrect_meta_Parent2 = GenderCorrection, GeneticSex_OtsSEXY3_Parent2 = GeneticSex_OtsSEXY3)

#and summarize sex for parent1 and parent2
juvs_COLONY_filter_Parent1_sex_final <- juvs_COLONY_filter_Par2_og_meta %>%
  mutate(., Parent1_Sex_2 = ifelse(is.na(Parent1_Sex_1), GeneticSex_OtsSEXY3_Parent1, Parent1_Sex_1)) %>% #use genetic sex if NA, otherwise stick with SNPPIT/COLONY informed sex
  mutate(., Parent1_Sex_final = ifelse(Parent1_Sex_2 == "?", Gender_meta_Parent1, Parent1_Sex_2)) %>% #if both snppit/COLONY and genetic sex unknown, use gender (phenotypic sex)
  relocate(., Parent1_Sex_final, .after = Parent1)

juvs_COLONY_filter_Parent2_sex_final <- juvs_COLONY_filter_Parent1_sex_final %>%
  mutate(., Parent2_Sex_2 = ifelse(is.na(Parent2_Sex_1), GeneticSex_OtsSEXY3_Parent2, Parent2_Sex_1)) %>% 
  mutate(., Parent2_Sex_final = ifelse(Parent2_Sex_2 == "?", Gender_meta_Parent2, Parent2_Sex_2)) %>% 
  relocate(., Parent2_Sex_final, .after = Parent2)

#then can remove the intermediate sex columns
juvs_COLONY_filter_final <- juvs_COLONY_filter_Parent2_sex_final %>%
  select(., -Parent1_Sex_1, -Parent1_Sex_2, -Parent2_Sex_1, -Parent2_Sex_2) %>%
  rename(., Parent1_Sex_ByCOLONY = Parent1_Sex, Parent2_Sex_ByCOLONY = Parent2_Sex)

#easiest to write to csv and look through assignments by eye to assure no non-sensical assignments (M-M or F-F pairs)
write_csv(juvs_COLONY_filter_final, "COLONY2_Results/Juvs_COLONY_assign_Prob_0.90_ParentSexData.csv")

```

Like with the adults, I then went through these assignments passing filter and check parental sex data to make sure the assignments were biologically plausible (which almost all were since it was informed by SNPPIT AND COLONY assignments). These accepted assignments are within the Juvs_COLONY_assign_filtered_ParSexAssigned.csv file and the final parental sex designations are within the Parent_Sex_Assign_by_COLONY_results.csv file. Eventually should use this file and the SNPPIT file to update sex info in Progeny. 

Ok now we are going to combine these filtered, parent sex assigned COLONY assignments to the snppit assignments. 

```{r}
rm(list = ls())
library(tidyverse)

#read in the processed COLONY assignments
juvs_all_COLONY_filter <- read_csv("COLONY2_Results/Juvs_COLONY_assign_filtered_ParSexAssigned.csv", col_types = cols(.default = "c"))

#read in the filtered and finalized SNPPIT trios
juvs_snppit_all <- read_csv("SNPPIT_run_files/FINAL_AllCollections_AcceptedTrios.csv", col_types = cols(.default = "c"))

#for combining with COLONY assignments, want to parse down to following columns
#and filter for just the juvenile assignments since that's what we're looking at from COLONY right now
juvs_snppit_all <- juvs_snppit_all %>%
  select(., FDR, Kid, Pa, Ma, Kid_LifeHistoryStage, Kid_SampleYear) %>%
  filter(., Kid_LifeHistoryStage == "Juvenile") %>%
  unite(., OffspCollection, Kid_LifeHistoryStage, Kid_SampleYear, sep = "_") %>%
  mutate(., AssignMethod = "snppit")

#want to combine this with the COLONY filtered assignments and just check concordance
#which should be pretty good since the SNPPIT trios were used to create known maternity/paternity relationships for COLONY
check <- left_join(juvs_snppit_all, juvs_all_COLONY_filter, by = c("Kid" = "OffspringID"))

#look for non-matching fathers amongst those assigned by both COLONY and SNPPIT
no_match_father <- filter(check, Pa != Sire)
#0 cases

#look for non-matching mothers amongst those assigned by both COLONY and SNPPIT
no_match_mother <- filter(check, Ma != Dam)
#0 cases

#now we only need to add in the assignments from COLONY that weren't found by snppit, since we know all the snppit trios were recovered by COLONY
new_COLONY_assign <- anti_join(juvs_all_COLONY_filter, juvs_snppit_all, by = c("OffspringID" = "Kid"))

#many of these are instances where COLONY assigned a generated, placeholder ID for both parents (i.e. parents were unsampled)
#several others are single father, and single mother assignments
#and then looks like it identified a few more trios
#first search for those assignments with unkown father, but known mother
juvs_unk_father <- new_COLONY_assign %>%
  filter(., grepl("\\*", Sire)) %>%
  filter(., !grepl("\\#", Dam))

#and then for unknown mothers, but known father
juvs_unk_mother <- new_COLONY_assign %>%
  filter(., grepl("\\#", Dam)) %>%
  filter(., !grepl("\\*", Sire))

#and last new trios (i.e., both parents sampled) (not nearly as many as for the adults, which were laregly broodstock parents)
juvs_trios <- new_COLONY_assign %>%
  filter(., !grepl("\\*", Sire)) %>%
  filter(., !grepl("\\#", Dam))

#curious how many distinct individuals the unknown parents in the single parent pairs represent
no_unk_fathers <- juvs_unk_father %>%
  group_by(., OffspringSampleYear) %>%
  summarise(Unique_Fathers = n_distinct(Sire))
#most in 2016-37 unique unsampled fathers

no_unk_mothers <- juvs_unk_mother %>%
  group_by(., OffspringSampleYear) %>%
  summarise(Unique_Mothers = n_distinct(Dam))
#most in 2013- 17 unique, unsampled mothers

#now combine the unknown father/mother and trio dataframes
juvs_COLONY <- bind_rows(juvs_unk_father, juvs_unk_mother, juvs_trios)

#need to reformat this COLONY single parent df so we can bind to snppit assignments
juvs_colony_keep <- juvs_COLONY %>%
  mutate(., AssignMethod = "colony") %>%
  rename(., Kid = OffspringID, Pa = Sire, Ma = Dam, OffspCollection = OffspringSampleYear) %>%
  select(., OffspCollection, Kid, Pa, Ma, Probability, AssignMethod)


#combine final snppit and colony assignments. All snppit assignments will have "NA" in the Probability column, and all COLONY assignments will have "NA" in the FDR and SpawnYear columns
#only select the shared columns
juvs_combine <- bind_rows(juvs_snppit_all, juvs_colony_keep) %>%
  select(., OffspCollection, FDR, Probability, AssignMethod, Kid, Pa, Ma)
  

save(juvs_combine, file ='COLONY2_Results/Juvs_SNPPIT_COLONY_filtered_assign.Rdata')
write_csv(juvs_combine, "COLONY2_Results/Juvs_SNPPIT_COLONY_filtered_assign.csv")
```


